Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-08 xrb2/paper.tex
some intro work

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
We continue to investigate laterally propagating flames in XRBs...

@@

Unlike our previous paper, all runs are now conducted without artificially boosting the speed of the flame in order to reduce the computational cost. This is possible because of the work done to offload the code to GPUs, where it runs significantly faster. We can therefore run the tests without any boosting.

>>>>

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
We continue to investigate laterally propagating flames in XRBs using
fully compressible hydrodynamics simulations.  In the current study we
relax the approximations used previously and explore the effect of
rotation rate and the thermal structure of the neutron star on the
flame.  We find that higher temperature atmospheres lead to faster
flames and observe acceleration of the flame front as it propagates
through the atmosphere.  All of the software used for these
simulations is freely available.

@@

Considerable evidence suggests that ignition in an X-ray burst starts
in a localized region and then spreads across the surface of the
neutron star~\citep{bhattacharyya:2007,chakraborty:2014}.  We continue
our study of flame spreading through fully compressible hydrodynamics
simulations of the flame.  Building on our previous
paper~\citep{flame_wave1}, we relax the approximations we made
previously (artificially boosting the speed of the flame in order to
reduce the computational cost) and explore how the flame properties
depend on rotation rate and the thermal structure of the neutron
star. This new set of realistic simulations is possible because of the
work done to offload our simulation code, \castro~\cite{castro_joss}, to GPUs, where it
runs significantly faster.
